On optimisation in HDR brachytherapy

### 2015-03-09 Paper BMT/article-sample-proceedings.tex
New Graphics and tables included

\documentclass[USenglish,twocolumn]{article}
\usepackage{etex}
\usepackage[utf8]{inputenc}
\usepackage[big,online]{dgruyter}
\usepackage{hypernat}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\setcitestyle{numbers,square,comma,sort&compress}

@@

\subsubsection{Weights}
It seems hard to examine a specific sets of weights, that is applicable to any type of patients. The experiment has shown, that a higher weighted treatment has a much higher runtime and the convergency decreases.

\subsubsection{Probabilities} 
The results have shown, that a high mutation rate leads to a very low tumor coverage. Furthermore the algorithm often doesn't converges, because the changes of the individuals accure too often. A stable state becomes less likely. \\ For the crossover rate the results showed, that the value should be between 0.7 and 0.9.

\subsubsection{Scaling and Accuracy}
The dose distribution of a radioactive seed shows that the dose at a radius of 10 cm is negligible small. So any treatment range higher than 10 cm wouldn't lead to better results anyway. (TODO: which range is acceptable)

>>>>

\documentclass[USenglish,twocolumn]{article}
\usepackage{etex}
\usepackage[utf8]{inputenc}
\usepackage[big,online]{dgruyter}
\usepackage{hypernat}
\usepackage{tikz}
\usetikzlibrary{shapes,arrows}
\usepackage{multirow}
\usepackage{pgfplots}
\usepackage{pgfplotstable}
\setcitestyle{numbers,square,comma,sort&compress}

@@

\subsubsection{Weights}
It seems hard to examine a specific sets of weights, that is applicable to any type of patients. The experiment has shown, that a higher weighted treatment has a much higher runtime and the convergency decreases.  
\begin{figure}[ht]
\caption{Difference between the goal dose and the average dose}
\begin{tikzpicture}
  \begin{axis}[
  	name=one,
  	width=0.86 \columnwidth,
  	height=1.0in, 
  	scale only axis,
  	xmajorticks=false,
  	xtick={0,10,20,30,40},
  	ytick={-20,-10,...,10},
  	minor ytick={-20,-15,...,10},
  	legend style={anchor=north,at={(0.5,1.4)},font=\small},
  	legend columns=2,
    xmin=0,
    xmax=40,
  	ymax = 5,
  	ymin = -20,
    grid=both,
    y label style={at={(axis description cs:0.1,.5)},anchor=south},
    ylabel = {Diff. to GD [Gy]}
    ]
	\addplot [color=black,dashed,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 -7.4061373\\
						20 -7.3660937\\
						30 -7.16107\\
						40 -7.5223036\\	};
	\addlegendentry{Bladder};

	\addplot [color=black,dotted,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 -6.6003648\\
						20 -7.250544\\
						30 -8.3557603\\
						40 -5.8634733\\ };
	\addlegendentry{Rectum};

	\addplot [color=black,dash pattern=on 7pt off 7pt,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 -17.7968793\\
						20 -16.8252388\\
						30 -17.5772547\\
						40 -15.4201025\\ };
	\addlegendentry{Urethra};

	\addplot [color=black,solid,line width=1.0pt]
	table[row sep=crcr]{0 0\\
	 					10 -1.0171151\\
	 					20 -1.1222384\\
				 		30 -1.0559538\\
	 					40  0.6725971\\};
	\addlegendentry{Tumor};					
  \node at (rel axis cs:1,1) [anchor=north east] {Bladder weighted};	
  \end{axis}

  \begin{axis}[
  	name=two,
  	width=0.86 \columnwidth,
  	height=1.0in, 
  	scale only axis,
  	at=(one.below south),
    anchor=above north,
  	xmajorticks=false,
  	xtick={0,10,20,30,40},
  	ytick={-20,-0,...,100},
  	minor ytick={-10,0,...,100},
    xmin=0,
    xmax=40,
  	ymax = 95,
  	ymin = -20,
    grid=both,
    y label style={at={(axis description cs:0.1,.5)},anchor=south},
    ylabel = {Diff. to GD [Gy]}
    ]
	\addplot [color=black,dashed,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 46.8163804\\
						20 -6.5099569\\
						30 -6.4596163\\
						40 45.5999754\\ };

	%\addlegendentry{Bladder};

	\addplot [color=black,dotted,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 46.4315353\\
						20 -7.0846292\\
						30 -8.312817\\
						40 44.4589502\\ };

	%\addlegendentry{Rectum};

	\addplot [color=black,dash pattern=on 7pt off 7pt,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 73.834936\\
						20 -16.600937\\
						30 -15.1440168\\
						40	80.79331\\  };
	%\addlegendentry{Urethra};

	\addplot [color=black,solid,line width=1.0pt]
	table[row sep=crcr]{0 0\\
	 					10 95.820661\\
	 					20 -0.5231224\\
	 					30 -1.3135843\\
	 					40	94.652913\\ };
	%\addlegendentry{Tumor};					
  \node at (rel axis cs:1,1) [anchor=north east] {Rectum weighted};	
  \end{axis}
  \begin{axis}[
  	name=three,
  	width=0.86 \columnwidth,
  	height=1.0in, 
  	scale only axis,
  	at=(two.below south),
    anchor=above north,
  	xmajorticks=false,
  	xtick={0,10,20,30,40},
  	ytick={-20,-0,...,100},
  	minor ytick={-10,0,...,100},
  	legend style={anchor=north,at={(0.5,1.3)},font=\small},
  	legend columns=2,
    xmin=0,
    xmax=40,
  	ymax = 95,
  	ymin = -20,
    grid=both,
    y label style={at={(axis description cs:0.1,.5)},anchor=south},
    ylabel = {Diff. to GD [Gy]}
    ]
	\addplot [color=black,dashed,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 46.8163804\\
						20 -6.5099569\\
						30 45.5999754\\
						40 -6.4596163\\ };

	%\addlegendentry{Bladder};

	\addplot [color=black,dotted,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 46.4315353\\
						20 -7.0846292\\
						30 44.4589502\\
						40 -8.312817\\ };

	%\addlegendentry{Rectum};

	\addplot [color=black,dash pattern=on 7pt off 7pt,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 73.834936\\
						20 -16.600937\\
						30 80.79331\\
						40 -15.1440168\\ };
	%\addlegendentry{Urethra};

	\addplot [color=black,solid,line width=1.0pt]
	table[row sep=crcr]{0 0\\
	 					10 95.820661\\
	 					20 -0.5231224\\
	 					30 94.652913\\
	 					40 -1.3135843\\ };
	%\addlegendentry{Tumor};					
  \node at (rel axis cs:1,1) [anchor=north east] {Urethra weighted};	
  \end{axis}
  \begin{axis}[
  	name=four,
  	width=0.86 \columnwidth,
  	height=1.0in, 
  	scale only axis,
  	at=(three.below south),
    anchor=above north,
  	xmajorticks=true,
  	xtick={0,10,20,30,40},
  	ytick={-20,-10,...,10},
  	minor ytick={-15,-10,...,5},
    xmin=0,
    xmax=40,
  	ymax = 10,
  	ymin = -20,
    grid=both,
    xlabel = {Weighting Factor},
    y label style={at={(axis description cs:0.1,.5)},anchor=south},
    ylabel = {Diff. to GD [Gy]}
    ]
	\addplot [color=black,dashed,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 -7.9814571\\
						20 -2.0920392\\
						30 -6.5044591\\
						40 -6.4056077\\ };

	%\addlegendentry{Bladder};

	\addplot [color=black,dotted,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 -8.2390329\\
						20 -3.2641176\\
						30 -6.7960123\\
						40 -6.5058489\\ };

	%\addlegendentry{Rectum};

	\addplot [color=black,dash pattern=on 7pt off 7pt,line width=1.0pt]
	table[row sep=crcr]{0 0\\
						10 -18.198227\\
						20 -6.5576085\\
						30 -18.4460054\\
						40 -16.7663932\\ };
	%\addlegendentry{Urethra};

	\addplot [color=black,solid,line width=1.0pt]
	table[row sep=crcr]{0 0\\
	 					10 -1.8981359\\
	 					20 7.2659238\\
	 					30 -0.6839885\\
	 					40 -0.955956\\ };
	%\addlegendentry{Tumor};					
  \node at (rel axis cs:1,1) [anchor=north east] {Tumor weighted};	
  \end{axis}

\end{tikzpicture}
\end{figure}

\subsubsection{Probabilities} 
The results have shown, that a high mutation rate leads to a very low tumor coverage. Furthermore the algorithm often doesn't converges, because the changes of the individuals accure too often. A stable state becomes less likely. \\ For the crossover rate the results showed, that the value should be between 0.7 and 0.9.
% Please add the following required packages to your document preamble:
% \usepackage{multirow}
\begin{table}[h]
\begin{tabular}{c|ccccc}
\textbf{MR}          & \textbf{CR :}     & 0.3   & 0.5   & 0.7   & 0.9   \\ \hline
\multirow{2}{*}{0.3} & \textbf{CI}       & 1,092 & 1,019 & 1,683 & 1,101 \\
                     & \textbf{Coverage} & 0,778 & 0,387 & 1,000 & 0,770 \\ \hline
\multirow{2}{*}{0.5} & \textbf{CI}       & 1,028 & 1,032 & 1,022 & 1,079 \\
                     & \textbf{Coverage} & 0,360 & 0,410 & 0,395 & 0,403 \\ \hline
\multirow{2}{*}{0.7} & \textbf{CI}       & 1,007 & 1,046 & 1,012 & 1,035 \\
                     & \textbf{Coverage} & 0,281 & 0,316 & 0,011 & 0,341 \\ \hline
\multirow{2}{*}{0.9} & \textbf{CI}       & 1,034 & 1,000 & 1,109 & 1,043 \\
                     & \textbf{Coverage} & 0,256 & 0,001 & 0,736 & 0,273 \\
\end{tabular}
\end{table}
\subsubsection{Scaling and Accuracy}
The dose distribution of a radioactive seed shows that the dose at a radius of 10 cm is negligible small. So any treatment range higher than 10 cm wouldn't lead to better results anyway. (TODO: which range is acceptable)
